---
name: Todd M.
surname: Ellis
position: "Data Analyst & Statistical Programmer"
profilepic: portrait--yee.jpg
address: |
         | Hobart, Tasmania, Australia
phone: +61 466 683 552
email: "toddellis.wa@gmail.com"
linkedin: tmichaelellis
orcid: 0000-0002-4410-8676
researchgate: Todd-Ellis-4
github: toddellis
twitter: tootstorm
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 44B0D1
output: 
  vitae::awesomecv:
    keep_tex: false
    page_total: true
always_allow_html: yes
header-includes:
  \usepackage{float}
  \usepackage{multicol}
  \usepackage{colortbl}
  \arrayrulecolor{white}
  \usepackage{hhline}
  \definecolor{light-gray}{gray}{0.95}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      cache = FALSE)

source(here::here('./scripts/base_data.R'))

## FONTS #### 
.uni <-
  fontawesome::fa('university')
.job <-
  fontawesome::fa('briefcase')
```

# PROFESSIONAL SUMMARY

 * I’m a data analyst and scientist with a background in the environmental sciences. I’ve worked in a variety of laboratory and field settings, coordinating research projects in academic, government, and industry settings. I’ve also maintained relational database systems for public and private organizations, developed novel mathematical tools and statistical models for critical management efforts, trained hundreds of students and volunteers in analytical methods and project design, and coordinated project efforts with public and industry managers.

# EDUCATION 

```{r}
EDUCATION |>
  detailed_entries(UNIVERSITY, DATES, DEGREE, LOCATION, THESIS,
                   .protect=FALSE)
```

# PROFESSIONAL EXPERIENCE

```{r}

PROFESSIONAL_EXPERIENCE |>
  # dplyr::filter(OUTPUT == 'resume') |>
  # dplyr::filter(dplyr::between(ID, max(ID) - 5, max(ID))) |>
  dplyr::group_by(desc(ID), INSTITUTION, DATES, POSITION) |>
  dplyr::slice(1:4) |>
  vitae::detailed_entries(INSTITUTION,
                          DATES,
                          POSITION,
                          LOCATION,
                          DESCRIPTION,
                          .protect = FALSE)

```

```{r}
# TEACHING EXPERIENCE ----
# N.B. Dropped for time being, consolidated into research experience and renamed to professional experience
# TEACHING_EXPERIENCE |>
#   # dplyr::filter(OUTPUT == 'resume') |>
#   # dplyr::group_by(desc(ID), INSTITUTION, DATES, POSITION) |>
#   # dplyr::slice(1:3) |>
#   vitae::detailed_entries(INSTITUTION,
#                           DATES,
#                           POSITION, 
#                           LOCATION,
#                           DESCRIPTION,
#                           .protect = FALSE)
```

# INDEPENDENT RESEARCH CONSULTING

```{r, results = "asis"}
CONSULTING %>%
  dplyr::arrange(desc(lubridate::as_date(paste0(DATE, '-01'))),
                 desc(readr::parse_number(AMOUNT))) %>%
  baretable(align='lllp{9.3cm}r',
            hline.after=c(0,NROW(.)),
            ## Default {10}{16}
            size="\\fontsize{6}{11}", 
            add.to.row=list(
              pos=as.list(seq(NROW(.))),
              command=rep("\\\\[-0.2cm]",NROW(.))))
```

# PUBLICATIONS

```{r}
vitae::bibliography_entries(here::here("./bib/bibliography--personal.bib")) |>
  dplyr::filter(type != '') |>
  dplyr::arrange(desc(issued),
                 desc(author$family))
```

# PACKAGES AND DATA

```{r}
vitae::bibliography_entries(here::here("./bib/bibliography--personal.bib")) |>
  dplyr::filter(type == '') |>
  dplyr::arrange(desc(issued),
                 desc(author$family))
```

```{r}
# # CONFERENCES AND PRESENTATIONS
# 
# * **Ellis, T.M.** 2021-10. Tasmania Analytics Project. Department of Education Lunch and Learn. Sandy Bay, Tasmania, Australia.
# * **Ellis, T.M.** 2020-03. Changes in moisture availability drive fire risk. Bushfire Risk Management Research Hub Researchers Meeting 220. Wollongong, New South Wales, Australia.
# * **Ellis, T.M.** 2016-06. Climatic Drivers of western spruce budworm outbreaks in the Okanogan Highlands. Western Washington University. Bellingham, Washington, USA. 
# * **Ellis, T.M.**, and Flower, A. 2016-04. Controlling factors of spruce budworm outbreaks in the Okanogan Highlands. American Association of Geographers. San Francisco, California, USA.
# * Pettit, J., Stachowiak, L., Sala, A., Pinnell, S., Sykora, J., & **Ellis, T.M.** 2014-07. Climate responses of *Pseudotsuga menziesii* and *Pinus flexilis* in the Greater Yellowstone (USA). North American Dendroecological Fieldweek. Cody, Wyoming, USA.
# * **Ellis, T.M.** 2014-05. Mapping alpine treeline: A comparative analysis of Structure-from-Motion and LiDAR techniques using digital aerial imagery. Western Washington University. Bellingham, Washington, USA. 
# * **Ellis, T.M.**, Huling, D., and McGee, C. 2014-04. Perceptions of risk in Bellingham, Washington. Association of Washington Geographers. Seattle, Washington, USA.
# * **Ellis, T.M.** 2013-12. Biogeographic implications of Structure-from-Motion imagery. Western Washington University. Bellingham, Washington, USA. 
# * **Ellis, T.M.** 2012-05. Wildfire hazard data for the Yellowstone National Park Ecosystem: 1987-1988. Texas State University. San Marcos, Texas, USA.
# * **Ellis, T.M.** 2012-04. Cretaceous-aged fossiliferous outcrops of the Big Bend region. Texas State University. San Marcos, Texas, USA.
# * **Ellis, T.M.**, and McDonnell, R. 2011-12. Predator-prey relations in the Greater Yellowstone Ecosystem. Texas State University. San Marcos, Texas, USA.
```

# HONOURS

```{r, results = "asis"}
HONOURS %>%
  dplyr::arrange(desc(lubridate::as_date(paste0(DATE, '-01'))),
                 desc(readr::parse_number(AMOUNT))) %>%
  baretable(align='llp{5.5cm}p{7.75cm}r',
            hline.after=c(0,NROW(.)),
            size="\\fontsize{10}{16}",
            add.to.row=list(
              pos=as.list(seq(NROW(.))),
              command=rep("\\\\[-0.2cm]",NROW(.))))
```

# MANUSCRIPT REVIEWER

* [Fire Ecology](https://link.springer.com/journal/42408)

# PRESS

* 2021-10-12: [Bushfire research team awarded prestigious Eureka Prize](https://www.utas.edu.au/communications/general-news/all-news/bushfire-research-team-awarded-prestigious-eureka-prize). University of Tasmania.
