---
name: Todd M.
surname: Ellis
position: "Data Analyst & Statistical Programmer"
profilepic: portrait--yee.jpg
address: |
         | Hobart, Tasmania, Australia
phone: +61 466 683 552
email: "toddellis.wa@gmail.com"
linkedin: tmichaelellis
orcid: 0000-0002-4410-8676
researchgate: Todd-Ellis-4
github: toddellis
twitter: tootstorm
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 44B0D1
output: 
  vitae::awesomecv:
    keep_tex: false
    page_total: true
always_allow_html: yes
header-includes:
  \usepackage{float}
  \usepackage{multicol}
  \usepackage{colortbl}
  \arrayrulecolor{white}
  \usepackage{hhline}
  \definecolor{light-gray}{gray}{0.95}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      cache = FALSE)

source(here::here('./scripts/base_data.R'))

## FONTS #### 
## Only needed if I end up keeping the map -- not sure I like that, however.
# .uni <-
#   fontawesome::fa('university')
# .job <-
#   fontawesome::fa('briefcase')
```

# PROFESSIONAL SUMMARY

I’m a data analyst and scientist with a background in forest ecology, physical geography, and higher education. I've worked as an analyst in a wide variety of laboratory, field, and office settings across the United States and Australia. Over the course of my career, I've developed novel mathematical tools and statistical models; maintained relational databases and statistical packages used for conducting data analysis and producing standardized reports; trained countless staff, students, and volunteers; and managed complex and critical projects. My research has been published in high-impact, peer-reviewed journals, and I'm also skilled at conveying complex data and information to both casual and experienced stakeholders.

# EDUCATION 

```{r}
EDUCATION |>
  ## Remove my TXState faux-thesis.
  ## N.B. This 'thesis' is really just the major, defining research project of my undergraduate which I simply want to remember for its impact.
  tidyr::unnest(THESIS) |>
  dplyr::mutate(THESIS = ifelse(INSTITUTION == 'Texas State University',
                                NA_character_,
                                THESIS)) |>
  vitae::detailed_entries(INSTITUTION, 
                          DATES, 
                          DEGREE,
                          embolden(LOCATION), 
                          THESIS,
                          .protect=FALSE)
```

# PROFESSIONAL EXPERIENCE

```{r}
## May want to filter out teaching aspects of WWU Graduate Teaching Assistant role here.
PROFESSIONAL_EXPERIENCE |>
  ## Remove those positions that don't quite fit
  dplyr::filter(!POSITION %in% c(
    ## Likely not relevant for most applications
    # "Substitute Teacher",
    ## If displaying a consulting section, don't need this
    "Independent Research Contractor"
  )) |>
  # tidyr::unnest(DESCRIPTION) |>
  # dplyr::group_by(INSTITUTION, DATES, POSITION) |>
  # dplyr::slice(1:4) |>
  # filter_latest("YEAR_END", 5) |>
  order_by_date() |>
  vitae::detailed_entries(paste0(INSTITUTION, ": ", DEPARTMENT, " (", TYPE, ")"),
                          DATES,
                          POSITION,
                          embolden(LOCATION),
                          DESCRIPTION,
                          .protect = FALSE)

```
<!-- May only be worth expanding and splitting from professional experience if pursuing a teaching academic position.
# TEACHING EXPERIENCE

```{r}
# N.B. Dropped for time being, consolidated into research experience and renamed to professional experience
TEACHING_EXPERIENCE |>
  # dplyr::filter(OUTPUT == 'resume') |>
  # dplyr::group_by(desc(ID), INSTITUTION, DATES, POSITION) |>
  # dplyr::slice(1:3) |>
  vitae::detailed_entries(INSTITUTION,
                          DATES,
                          POSITION,
                          LOCATION,
                          DESCRIPTION,
                          .protect = FALSE)
```
-->

# VOLUNTEER EXPERIENCE

```{r}
VOLUNTEER_EXPERIENCE |>
  order_by_date() |>
  # filter_latest("YEAR_END", 5) |>
  # dplyr::arrange(desc(YEAR_START)) |>
  vitae::detailed_entries(INSTITUTION,
                          DATES,
                          POSITION,
                          embolden(LOCATION),
                          .protect = FALSE)
```

# PUBLICATIONS

## JOURNAL ARTICLES

```{r}
# gprofile <- 
#   rvest::read_html("https://scholar.google.com/citations?user=q6vTAroAAAAJ")
# 
# rvest::html_nodes(gprofile, ".gsc_a_h") |>
#   rvest::html_text() %>%
#   .[2:length(.)]|>
#   dplyr::bind_cols(rvest::html_nodes(gprofile, ".gsc_a_at") |>
#                      rvest::html_text()) |>
#   dplyr::bind_cols(rvest::html_nodes(gprofile, ".gsc_a_ac") |>
#                      rvest::html_text()) |>
#   dplyr::bind_cols(rvest::html_nodes(gprofile, ".gs_gray") |>
#                      rvest::html_text() %>%
#                      .[seq(2, length(.), by = 2)] %>%
#                      .[2:length(.)]) |>
#   dplyr::transmute(TITLE = `...2`,
#                    DATE = as.numeric(`...1`),
#                    CITATIONS = as.numeric(`...3`),
#                    JOURNAL = stringr::str_remove_all(`...4`, "[,-.\\(\\)[0-9]]") |>
#                      stringr::str_trim() |>
#                      tools::toTitleCase()) |>
#   dplyr::mutate(JOURNAL = ifelse(JOURNAL %in% c("University of Tasmania", "Western Washington University"),
#                                  paste0(JOURNAL, " (thesis)"),
#                                  JOURNAL)) |>
#   dplyr::arrange(desc(DATE), JOURNAL) |>
#   vitae::brief_entries(ifelse(!is.na(CITATIONS) & CITATIONS > 0,
#                               glue::glue("\\textbf{<TITLE>} \\newline via \\textit{<JOURNAL>}: <CITATIONS> <ifelse(CITATIONS == 1, 'citation', 'citations')> as of <format(Sys.Date(), format = '%Y %B')>",
#                                   .open = "<",
#                                   .close = ">"),
#                               glue::glue("\\textbf{<TITLE>} \\newline \\textit{<JOURNAL>}",
#                                          .open = "<",
#                                          .close = ">")),
#                        paste0(DATE, "\\newline"),
#                        # embolden(JOURNAL), 
#                        .protect = FALSE)

BIBLIOGRAPHY |>
  dplyr::filter(TYPE == "journal-article") |>
  order_by_date() |>
  vitae::brief_entries(glue::glue("\\textbf{<TITLE>} \\newline \\textit{<JOURNAL>}. \\underline{\\href{<DOI_URL>}{<DOI_URL>}}",
                                  .open = "<",
                                  .close = ">"),
                       paste0(substr(DATE, 1, 7), "\\newline"),
                       # paste0(substr(DATE, 1, 7)),
                       # embolden(JOURNAL), 
                       .protect = FALSE)
  
# vitae::bibliography_entries(here::here("./bib/bibliography--personal.bib")) |>
#   dplyr::filter(type != '') |>
#   dplyr::arrange(desc(issued),
#                  desc(author$family))
```

## THESES

```{r}
BIBLIOGRAPHY |>
  dplyr::filter(TYPE == "dissertation-thesis") |>
  # dplyr::mutate(TITLE = ifelse(TYPE == 'dissertation-thesis',
  #                              paste0(TITLE, " (graduate thesis)"),
  #                              TITLE)) |>
  order_by_date() |>
  vitae::brief_entries(glue::glue("\\textbf{<TITLE>} \\newline \\textit{<JOURNAL>}. \\underline{\\href{<DOI_URL>}{<DOI_URL>}}",
                                  .open = "<",
                                  .close = ">"),
                       paste0(substr(DATE, 1, 7), "\\newline"),
                       # paste0(substr(DATE, 1, 7)),
                       # embolden(JOURNAL), 
                       .protect = FALSE)
```


## OPEN-ACCESS DATA

```{r}
# vitae::bibliography_entries(here::here("./bib/bibliography--personal.bib")) |>
#   # dplyr::filter(type == '') |>
#   dplyr::filter(tolower(publisher) %in% c('figshare')) |>
#   dplyr::arrange(desc(issued),
#                  desc(author$family))
# 
# BIBLIO <- 
#   rvest::read_html("https://orcid.org/0000-0002-4410-8676")
# 
# BIBLIO |>
#   rvest::html_nodes("secondary-text") |>
#   rvest::html_text()

BIBLIOGRAPHY |>
  dplyr::filter(TYPE == "data-set") |>
  order_by_date() |>
  vitae::brief_entries(glue::glue("\\textbf{<TITLE>} \\newline \\textit{<JOURNAL>}. \\underline{\\href{<DOI_URL>}{<DOI_URL>}}",
                                  .open = "<",
                                  .close = ">"),
                       paste0(substr(DATE, 1, 7), "\\newline"),
                       # paste0(substr(DATE, 1, 7)),
                       # embolden(JOURNAL), 
                       .protect = FALSE)
  
```

## SOFTWARE

```{r}
# "\\textbf{<TITLE>}: <DESCRIPTION> \\newline 
#                                   via \\textit{\\underline{\\href{<URL>}{GitHub}}} 
#                                   (<ifelse(TYPE == 'private', glue::glue('last updated {DATE_END}: private'), glue::glue('last updated {DATE_END}'))>)"
BIBLIO_R |>
  dplyr::arrange(desc(DATE_START), TITLE) |>
  vitae::brief_entries(dplyr::case_when(TYPE == 'public' & !is.na(DATE_END) ~
                                          glue::glue("\\textbf{<TITLE>}: <DESCRIPTION> \\newline <SRC>. \\underline{\\href{<URL>}{<URL>}} (last updated <DATE_END>)",
                                                     .open = "<",
                                                     .close = ">"),
                                        TYPE == 'public' & is.na(DATE_END) ~
                                          glue::glue("\\textbf{<TITLE>}: <DESCRIPTION> \\newline <SRC>. \\underline{\\href{<URL>}{<URL>}}",
                                                     .open = "<",
                                                     .close = ">"),
                                        TRUE ~ 
                                          glue::glue("\\textbf{<TITLE>}: <DESCRIPTION> \\newline <SRC>. \\underline{<TYPE>}",
                                                     .open = "<",
                                                     .close = ">")),
                       paste0(DATE_START, "\\newline"),
                       .protect = FALSE)
# vitae::bibliography_entries(here::here("./bib/bibliography--personal.bib")) |>
#   # dplyr::filter(type == '') |>
#   dplyr::filter(stringr::str_detect(tolower(note), "r package")) |>
#   dplyr::arrange(title)
# BIBLIO_R |>
#   vitae::brief_entries(glue::glue("\\textbf{<PKG>}: <ROLE> \\newline <DESCRIPTION>", 
#                                   .open = "<", 
#                                   .close = ">"), 
#                        paste0(DATE, "\\newline"),
#                        .protect = FALSE)

```

# CONSULTING

## RESEARCH

```{r, results = "asis"}
CONSULTING_EXPERIENCE |>
  order_by_date() |>
  ## Because FDL belongs more in Honours than IRC...
  # dplyr::filter(AGENCY != "Frontier Development Lab") |>
  # dplyr::arrange(desc(lubridate::as_date(paste0(DATE, '-01'))),
                 # desc(readr::parse_number(AMOUNT))) |>
  vitae::brief_entries(glue::glue("\\textbf{<PROJECT>} \\newline <AGENCY>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       embolden(AMOUNT),
                       .protect = FALSE)
```

## MANUSCRIPT REVIEWER

```{r}
tibble::tribble(
  ~ JOURNAL, ~ URL, ~TYPE, ~ DATE_START, ~ DATE_END, ~ ARTICLES,
  "Fire Ecology", "https://fireecology.springeropen.com/", "Open access", "2019-01", "2019-05", c(
    "https://fireecology.springeropen.com/articles/10.1186/s42408-019-0043-y"
    )
) |>
  dplyr::group_by(JOURNAL) |>
  dplyr::mutate(N_REVIEWS = length(unlist(ARTICLES))) |>
  dplyr::ungroup() |>
  order_by_date() |>
  vitae::brief_entries(glue::glue("\\textbf{\\textit{<JOURNAL>}} (<TYPE>: <URL>) \\newline <N_REVIEWS> <ifelse(N_REVIEWS == 1, 'article', 'articles')> since <substr(DATE_START, 1, 4)>",
                                  .open = "<",
                                  .close = ">"),
                       paste0("\\newline"),
                       "",
                       .protect = FALSE)
```

# OUTREACH

## CONFERENCES AND PRESENTATIONS

```{r}
OUTREACH |>
  dplyr::filter(TYPE %in% c(
    "professional", "academic", "conference"
  )) |>
  tidyr::unnest(c(URL, URL_TYPE)) |>
  dplyr::group_by(TITLE) |> 
  dplyr::slice(1) |>
  dplyr::ungroup() |>
  dplyr::mutate(LOCATION = stringr::str_remove(LOCATION, "(, Australia|, USA)")) |>
  order_by_date() |>
  vitae::brief_entries(dplyr::case_when(!is.na(EVENT) & !is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <EVENT> (\\underline{\\href{<URL>}{<URL_TYPE>}})", 
                                                                                 .open = "<", 
                                                                                 .close = ">"),
                                        is.na(EVENT) & !is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <AGENCY> (\\underline{\\href{<URL>}{<URL_TYPE>}})",
                                                                                .open = "<",
                                                                                .close = ">"),
                                        !is.na(EVENT) & is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <EVENT>",
                                                                                .open = "<",
                                                                                .close = ">"),
                                        TRUE ~ glue::glue("\\textbf{<TITLE>} \\newline <AGENCY>", 
                                                          .open = "<", 
                                                          .close = ">")),
                       paste0(substr(DATE, 1, 7), "\\newline"),
                       embolden(LOCATION),
                       .protect = FALSE)
```

## PRESS

```{r}
OUTREACH |>
  dplyr::filter(TYPE %in% c(
    "press"
  )) |>
  dplyr::mutate(LOCATION = stringr::str_remove(LOCATION, "(, Australia|, USA)")) |>
  vitae::brief_entries(glue::glue("\\textbf{<TITLE>} \\newline <AGENCY> (\\underline{\\href{<URL>}{<URL_TYPE>}})",
                                  .open = "<",
                                  .close = ">"),
                       paste0(substr(DATE, 1, 7), "\\newline"),
                       .protect = FALSE)
```

## COURSEWORK

```{r}

OUTREACH |>
  dplyr::filter(TYPE %in% c(
    "coursework"
  )) |>
  tidyr::unnest(c(URL, URL_TYPE)) |>
  dplyr::group_by(TITLE) |> 
  dplyr::slice(1) |>
  dplyr::ungroup() |>
  dplyr::mutate(LOCATION = stringr::str_remove(LOCATION, "(, Australia|, USA)")) |>
  order_by_date() |>
  vitae::brief_entries(dplyr::case_when(!is.na(EVENT) & !is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <EVENT> (\\underline{\\href{<URL>}{<URL_TYPE>}})", 
                                                                                 .open = "<", 
                                                                                 .close = ">"),
                                        is.na(EVENT) & !is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <AGENCY> (\\underline{\\href{<URL>}{<URL_TYPE>}})",
                                                                                .open = "<",
                                                                                .close = ">"),
                                        !is.na(EVENT) & is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <EVENT>",
                                                                                .open = "<",
                                                                                .close = ">"),
                                        TRUE ~ glue::glue("\\textbf{<TITLE>} \\newline <AGENCY>", 
                                                          .open = "<", 
                                                          .close = ">")),
                       paste0(substr(DATE, 1, 7), "\\newline"),
                       embolden(LOCATION),
                       .protect = FALSE)
```

# HONOURS

## AWARDS

```{r, results = "asis"}
HONOURS |>
  dplyr::filter(TYPE == 'award') |>
  order_by_date() |>
  # dplyr::arrange(desc(lubridate::as_date(paste0(DATE, '-01'))),
  #                desc(readr::parse_number(AMOUNT)))  |>
  vitae::brief_entries(glue::glue("\\textbf{<HONOUR>} \\newline <AGENCY>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       ifelse(!is.na(AMOUNT),
                              embolden(AMOUNT),
                              paste0("")),
                       .protect = FALSE)
```

## GRANTS AND SCHOLARSHIPS

```{r}
HONOURS |>
  dplyr::filter(TYPE %in% c('grant', 'scholarship')) |>
  order_by_date() |>
  # dplyr::arrange(desc(lubridate::as_date(paste0(DATE, '-01'))),
                 # desc(readr::parse_number(AMOUNT)))  |>
  vitae::brief_entries(glue::glue("\\textbf{<HONOUR>} \\newline <AGENCY>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       ifelse(!is.na(AMOUNT),
                              embolden(AMOUNT),
                              paste0("")),
                       .protect = FALSE)
```

