---
name: Todd M.
surname: Ellis
position: "Data Analyst & Statistical Programmer"
profilepic: portrait--yee.jpg
address: |
         | Hobart, Tasmania, Australia
phone: +61 466 683 552
email: "toddellis.wa@gmail.com"
linkedin: tmichaelellis
orcid: 0000-0002-4410-8676
researchgate: Todd-Ellis-4
github: toddellis
twitter: tootstorm
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 44B0D1
output: 
  vitae::awesomecv:
    keep_tex: false
    page_total: true
always_allow_html: yes
header-includes:
  \usepackage{float}
  \usepackage{multicol}
  \usepackage{colortbl}
  \arrayrulecolor{white}
  \usepackage{hhline}
  \definecolor{light-gray}{gray}{0.95}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      cache = FALSE)

source(here::here('./scripts/base_data.R'))

## FONTS #### 
.uni <-
  fontawesome::fa('university')
.job <-
  fontawesome::fa('briefcase')
```

# PROFESSIONAL SUMMARY

I’m a data analyst and scientist with a background in forest ecology, physical geography, and higher education. I've worked as an analyst in a wide variety of laboratory, field, and office settings across the United States and Australia. Across these experiences for public and private organisations, I've developed novel mathematical tools and statistical models; maintained relational databases and statistical packages used for conducting data analysis and producing standardised reports; trained countless staff, students, and volunteers; and managed complex and critical projects. My research has been published in high-impact, peer-reviewed journals, but I'm also skilled at conveying complex data and information to both casual and experienced stakeholders.

# EDUCATION 

```{r}
EDUCATION |>
  vitae::detailed_entries(UNIVERSITY, 
                          DATES, 
                          DEGREE,
                          embolden(LOCATION), 
                          THESIS,
                          .protect=FALSE)
```

# PROFESSIONAL EXPERIENCE

```{r}

PROFESSIONAL_EXPERIENCE |>
  # dplyr::filter(OUTPUT == 'resume') |>
  # dplyr::filter(dplyr::between(ID, max(ID) - 7, max(ID))) |>
  filter_latest("YEAR_END", 5) |>
  dplyr::group_by(desc(ID), INSTITUTION, DATES, POSITION) |>
  dplyr::slice(1:4) |>
  vitae::detailed_entries(INSTITUTION,
                          DATES,
                          POSITION,
                          embolden(LOCATION),
                          DESCRIPTION,
                          .protect = FALSE)

```

<!-- # TEACHING EXPERIENCE

```{r}
# TEACHING EXPERIENCE ----
# N.B. Dropped for time being, consolidated into research experience and renamed to professional experience
# TEACHING_EXPERIENCE |>
#   # dplyr::filter(OUTPUT == 'resume') |>
#   # dplyr::group_by(desc(ID), INSTITUTION, DATES, POSITION) |>
#   # dplyr::slice(1:3) |>
#   vitae::detailed_entries(INSTITUTION,
#                           DATES,
#                           POSITION, 
#                           LOCATION,
#                           DESCRIPTION,
#                           .protect = FALSE)
```

-->
<!--
# PUBLICATIONS

## ACADEMIC

```{r}
vitae::bibliography_entries(here::here("./bib/bibliography--personal.bib")) |>
  dplyr::filter(type != '') |>
  dplyr::arrange(desc(issued),
                 desc(author$family))
```

## OPEN-ACCESS DATA

```{r}
vitae::bibliography_entries(here::here("./bib/bibliography--personal.bib")) |>
  # dplyr::filter(type == '') |>
  dplyr::filter(tolower(publisher) %in% c('figshare')) |>
  dplyr::arrange(desc(issued),
                 desc(author$family))
```

## SOFTWARE

```{r}
vitae::bibliography_entries(here::here("./bib/bibliography--personal.bib")) |>
  # dplyr::filter(type == '') |>
  dplyr::filter(stringr::str_detect(tolower(note), "r package")) |>
  dplyr::arrange(title)
# BIBLIO_R |>
#   vitae::brief_entries(glue::glue("\\textbf{<PKG>}: <ROLE> \\newline <DESCRIPTION>", 
#                                   .open = "<", 
#                                   .close = ">"), 
#                        paste0(DATE, "\\newline"),
#                        .protect = FALSE)

```
-->
<!-- # CONFERENCES AND PRESENTATIONS

```{r}
# # CONFERENCES AND PRESENTATIONS
PRESENTATIONS |> 
  dplyr::filter(lubridate::year(lubridate::as_date(paste0(DATE, "-01"))) >= 2014) |>
  dplyr::arrange(desc(lubridate::as_date(paste0(DATE, '-01'))),
                 PRESENTATION) |>
  vitae::brief_entries(glue::glue("\\textbf{<PRESENTATION>} \\newline <AGENCY>, <LOCATION>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       # glue::glue("\\textbf{<LOCATION>}",
                       #            .open = "<",
                       #            .close = ">"),
                       .protect = FALSE)
```
-->
# CONSULTING

```{r, results = "asis"}
CONSULTING |>
  ## Because FDL belongs more in Honours than IRC...
  dplyr::filter(AGENCY != "Frontier Development Lab") |>
  dplyr::arrange(desc(lubridate::as_date(paste0(DATE, '-01'))),
                 desc(readr::parse_number(AMOUNT))) |>
  vitae::brief_entries(glue::glue("\\textbf{<PROJECT>} \\newline <AGENCY>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       glue::glue("\\textbf{<AMOUNT>}",
                                  .open = "<",
                                  .close = ">"),
                       .protect = FALSE)
```

# HONOURS

```{r, results = "asis"}
HONOURS |>
  # dplyr::filter(TYPE == 'award') |>
  filter_latest("YEAR", 5) |>
  dplyr::arrange(desc(lubridate::as_date(paste0(DATE, '-01'))),
                 desc(readr::parse_number(AMOUNT)))  |>
  vitae::brief_entries(glue::glue("\\textbf{<HONOUR>} \\newline <AGENCY>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       ifelse(!is.na(AMOUNT),
                              glue::glue("\\textbf{<AMOUNT>}",
                                         .open = "<",
                                         .close = ">"),
                              paste0("")),
                       .protect = FALSE)
```
<!--
## AWARDS

```{r, results = "asis"}
HONOURS |>
  dplyr::filter(TYPE == 'award') |>
  dplyr::arrange(desc(lubridate::as_date(paste0(DATE, '-01'))),
                 desc(readr::parse_number(AMOUNT)))  |>
  vitae::brief_entries(glue::glue("\\textbf{<HONOUR>} \\newline <AGENCY>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       ifelse(!is.na(AMOUNT),
                              glue::glue("\\textbf{<AMOUNT>}",
                                         .open = "<",
                                         .close = ">"),
                              paste0("")),
                       .protect = FALSE)
# baretable(align='llp{5.5cm}p{7.75cm}r',
  #           hline.after=c(0,NROW(.)),
  #           size="\\fontsize{5}{2}",
  #           add.to.row=list(
  #             pos=as.list(seq(NROW(.))),
  #             command=rep("\\\\[-0.2cm]",NROW(.))))
```

## GRANTS AND SCHOLARSHIPS

```{r}
HONOURS |>
  dplyr::filter(TYPE %in% c('grant', 'scholarship')) |>
  dplyr::arrange(desc(lubridate::as_date(paste0(DATE, '-01'))),
                 desc(readr::parse_number(AMOUNT)))  |>
  vitae::brief_entries(glue::glue("\\textbf{<HONOUR>} \\newline <AGENCY>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       ifelse(!is.na(AMOUNT),
                              glue::glue("\\textbf{<AMOUNT>}",
                                         .open = "<",
                                         .close = ">"),
                              paste0("")),
                       .protect = FALSE)
```
-->
# VOLUNTEER EXPERIENCE

```{r}
VOLUNTEER_EXPERIENCE |>
  # dplyr::filter(YEAR_END >= lubridate::year(Sys.Date()) - 5) |>
  filter_latest("YEAR_END", 5) |>
  dplyr::arrange(desc(YEAR_START)) |>
  vitae::detailed_entries(INSTITUTION,
                          DATES,
                          POSITION,
                          embolden(LOCATION),
                          .protect = FALSE)
  # vitae::brief_entries(glue::glue("\\textbf{<POSITION>} \\newline <INSTITUTION>",
  #                                 .open = "<",
  #                                 .close = ">"),
  #                      paste0(DATES, "\\newline"),
  #                      glue::glue("\\textbf{<LOCATION>}",
  #                                 .open = "<",
  #                                 .close = ">"),
  #                      .protect = FALSE)
```
<!--

# MANUSCRIPT REVIEWER

* [Fire Ecology](https://link.springer.com/journal/42408)

# PRESS

* 2021-10-12: [Bushfire research team awarded prestigious Eureka Prize](https://www.utas.edu.au/communications/general-news/all-news/bushfire-research-team-awarded-prestigious-eureka-prize). University of Tasmania.
-->
