---
name: Todd M.
surname: Ellis
position: "Data Analyst & Statistical Programmer"
profilepic: portrait--yee.jpg
address: |
         | Greater Hobart Region, Tasmania, Australia
         | `r format(Sys.time(), '%B %Y')`
aboutme: ""
phone: +61 466 683 552
email: "toddellis.wa@gmail.com"
linkedin: tmichaelellis
googlescholar: q6vTAroAAAAJ
orcid: 0000-0002-4410-8676
researchgate: Todd-Ellis-4
github: toddellis
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 44B0D1
docname: "Curriculum Vitae"
output: 
  vitae::awesomecv:
    keep_tex: false
    page_total: true
always_allow_html: yes
header-includes:
  \usepackage{float}
  \usepackage{multicol}
  \usepackage{colortbl}
  \usepackage{hhline}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      cache = FALSE)

source(here::here('./scripts/base_data.R'))
# twitter: tootstorm
```

# PROFESSIONAL SUMMARY 

I’m a data analyst and early career researcher with a varied background in forest ecology, pyrogeography, climate change, geospatial science, and higher education. I've worked as an analyst and researcher in a variety of laboratory, field, and office settings throughout the United States and Australia. Over the course of my career, I've developed novel mathematical tools and statistical models; maintained relational databases and statistical packages used for conducting data analysis and producing standardized reports; trained countless staff, students, and volunteers in institutional policies and procedures, as well as methodological approaches to statistical analysis; and managed both complex and transformative projects for higher education, government agencies, and private industry. My research has been published in high-impact, peer-reviewed journals, and I'm also skilled at conveying complex data and information to both casual and experienced stakeholders. 

As at `r Sys.Date()`, I have `r ACADEMIC_SUMMARY$pub_count` peer-reviewed publications including `r ACADEMIC_SUMMARY$pub_count_first` first-author publications. I have received a total of `r ACADEMIC_SUMMARY$citations_scopus` or `r ACADEMIC_SUMMARY$citations_gscholar` citations with an h-index of `r ACADEMIC_SUMMARY$h_scopus` or `r ACADEMIC_SUMMARY$h_gscholar` based on Scopus and Google Scholar, respectively.

# EDUCATION 

```{r}
EDUCATION |>
  tidyr::unnest(THESIS) |>
  dplyr::mutate(THESIS = ifelse(INSTITUTION == 'Texas State University',
                                NA_character_,
                                THESIS)) |>
  vitae::detailed_entries(INSTITUTION, 
                          DATES, 
                          DEGREE,
                          embolden(LOCATION), 
                          THESIS,
                          .protect=FALSE)
```

# PROFESSIONAL EXPERIENCE

```{r}
PROFESSIONAL_EXPERIENCE |>
  dplyr::filter(!POSITION %in% c(
    "Independent Research Contractor"
  )) |>
  dplyr::mutate(POSITION_NO = dplyr::row_number()) |> 
  tidyr::unnest(DESCRIPTION) |>
  dplyr::group_by(INSTITUTION, DEPARTMENT, TYPE, DATES, POSITION, LOCATION) |>
  dplyr::slice(1:4) |>
  # tidyr::nest(DESCRIPTION = DESCRIPTION) |> 
  dplyr::ungroup() |>
  filter_latest("YEAR_END", 3) |>
  order_by_date() |>
  dplyr::filter(POSITION_NO <= 3) |>
  vitae::detailed_entries(paste0(INSTITUTION, ": ", DEPARTMENT, " (", TYPE, ")"),
                          DATES,
                          POSITION,
                          embolden(LOCATION),
                          DESCRIPTION,
                          .protect = FALSE) |> 
  suppressWarnings()

```

# PUBLICATIONS

```{r}
SCOPUS |>
  dplyr::filter(aggregation_type == "Journal",
                !subtype_description %in% c("Book Chapter",
                                            "Conference Paper",
                                            "Erratum")) |>
  ## N.B. Probably something to update over time as I publish more, but these steps are a way to:
  ##      a) Limit the article count to 3-5 to ensure we're maintaining 2 pages
  ##      b) Pull only the most cited publications within a specified timeframe
  dplyr::mutate(DATE = substr(cover_date, 1, 7)) |>
  filter_latest("DATE",
                n = 7) |>
  dplyr::arrange(desc(citedby_count)) |>
  dplyr::slice(1:3) |>
  order_by_date() |>
  vitae::brief_entries(what = glue::glue("{<authors>} ({<substr(cover_date, 1, 4)>}). {<title>}. \\textit{<publication_name>}{<dplyr::case_when(!is.na(volume) & is.na(issue_identifier) ~ glue::glue(', {volume}'), !is.na(volume) & !is.na(issue_identifier) ~ glue::glue(', {volume}({issue_identifier})'), TRUE ~ '')>}{<dplyr::case_when(!is.na(page_range) ~ glue::glue(', {page_range}'), is.na(page_range) & !is.na(article_number) ~ glue::glue(', {article_number}'), TRUE ~ '')>}. \\underline{\\href{<paste0('https://doi.org/', doi)>}{<paste0('doi:', doi)>}}",
                                         .open = "<",
                                         .close = ">"),
                       when = entry_number,
                       with = embolden(glue::glue("{citedby_count} citations")),
                       .protect = FALSE)

```

# CONSULTING

## RESEARCH

```{r, results = "asis"}
CONSULTING_EXPERIENCE |>
  order_by_date() |>
  vitae::brief_entries(glue::glue("\\textbf{<PROJECT>} \\newline <AGENCY>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       embolden(AMOUNT),
                       .protect = FALSE)
```

## MANUSCRIPT REVIEWER

```{r}
tibble::tribble(
  ~ JOURNAL, ~ URL, ~TYPE, ~ DATE_START, ~ DATE_END, ~ ARTICLES,
  "Fire Ecology", "https://fireecology.springeropen.com/", "Open access", "2019-01", "2019-05", c("https://fireecology.springeropen.com/articles/10.1186/s42408-019-0043-y"),
  "Earth's Future", "https://agupubs.onlinelibrary.wiley.com/journal/23284277", "", "2022-09", "2022-10", c("2022EF002806R"),
  "Global Change Biology", "https://onlinelibrary.wiley.com/journal/13652486", "", "2022-10", "2022-10", c("GCB-22-2073"),
  "New Phytologist", "https://nph.onlinelibrary.wiley.com/journal/14698137", "", "2022-11", "2022-11", c("NPH-MS-2022-41630"),
  "Climatic Change", "https://www.springer.com/journal/10584", "", "2023-06", "2023-07", c("CLIM-D-23-00438")
) |>
  dplyr::group_by(JOURNAL) |>
  dplyr::mutate(N_REVIEWS = length(unlist(ARTICLES))) |>
  dplyr::ungroup() |>
  order_by_date() |>
  dplyr::arrange(JOURNAL) |>
  dplyr::mutate(NEW_TITLE = glue::glue("\\underline{\\textbf{\\textit{\\href{<URL>}{<JOURNAL>}}}}",# (since <DATE_START>)",
                                  .open = "<",
                                  .close = ">")) |>
  dplyr::summarise(NEW_TITLE = paste(NEW_TITLE, collapse = ", ")) |>
  vitae::brief_entries(NEW_TITLE,
                       .protect = FALSE)
  # dplyr::pull(NEW_TITLE) |>
  # paste0(collapse = ", ")
```

# HONOURS

## GRANTS, SCHOLARSHIPS AND AWARDS

```{r}
HONOURS |>
  order_by_date() |>
  filter_latest("DATE", n = 5) |>
  dplyr::filter(!is.na(AMOUNT)) |>
  vitae::brief_entries(glue::glue("\\textbf{<HONOUR>} \\newline <AGENCY>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       ifelse(!is.na(AMOUNT),
                              embolden(AMOUNT),
                              paste0("")),
                       .protect = FALSE)
```

# OUTREACH

## CONFERENCES AND PRESENTATIONS

```{r}
OUTREACH |>
  dplyr::filter(TYPE %in% c(
    "academic", 
    "conference"
  )) |>
  tidyr::unnest(c(URL, URL_TYPE)) |>
  dplyr::group_by(TITLE) |> 
  dplyr::slice(1) |>
  dplyr::ungroup() |>
  dplyr::mutate(LOCATION = stringr::str_remove(LOCATION, "(, Australia|, USA)")) |>
  order_by_date() |> 
  filter_latest("DATE", n = 5) |> 
  vitae::brief_entries(dplyr::case_when(!is.na(EVENT) & !is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <EVENT> (\\underline{\\href{<URL>}{<URL_TYPE>}})", 
                                                                                 .open = "<", 
                                                                                 .close = ">"),
                                        is.na(EVENT) & !is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <AGENCY> (\\underline{\\href{<URL>}{<URL_TYPE>}})",
                                                                                .open = "<",
                                                                                .close = ">"),
                                        !is.na(EVENT) & is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <EVENT>",
                                                                                .open = "<",
                                                                                .close = ">"),
                                        TRUE ~ glue::glue("\\textbf{<TITLE>} \\newline <AGENCY>", 
                                                          .open = "<", 
                                                          .close = ">")),
                       paste0(substr(DATE, 1, 7), "\\newline"),
                       embolden(LOCATION),
                       .protect = FALSE)
```

