---
name: Todd M.
surname: Ellis
position: "Data Analyst & Statistical Programmer"
profilepic: portrait--yee.jpg
address: |
         | Greater Hobart Region, Tasmania, Australia
         | `r format(Sys.time(), '%B %Y')`
aboutme: ""
phone: +61 466 683 552
email: "toddellis.wa@gmail.com"
linkedin: tmichaelellis
googlescholar: q6vTAroAAAAJ
orcid: 0000-0002-4410-8676
researchgate: Todd-Ellis-4
github: toddellis
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 44B0D1
docname: "Curriculum Vitae"
output: 
  vitae::awesomecv:
    keep_tex: false
    page_total: true
always_allow_html: yes
header-includes:
  \usepackage{float}
  \usepackage{multicol}
  \usepackage{colortbl}
  \usepackage{hhline}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      cache = FALSE)

source(here::here('./scripts/base_data.R'))
```

# PROFESSIONAL SUMMARY 

I’m a data analyst and early career researcher with a varied background in forest ecology, pyrogeography, climate change, geospatial science, and higher education. I've worked as an analyst and researcher in a variety of laboratory, field, and office settings throughout the United States and Australia. Over the course of my career, I've developed novel mathematical tools and statistical models; maintained relational databases and statistical packages used for conducting data analysis and producing standardized reports; trained countless staff, students, and volunteers in institutional policies and procedures, as well as methodological approaches to statistical analysis; and managed both complex and transformative projects for higher education, government agencies, and private industry. My research has been published in high-impact, peer-reviewed journals, and I'm also skilled at conveying complex data and information to both casual and experienced stakeholders. 

As at `r Sys.Date()`, I have `r ACADEMIC_SUMMARY$pub_count` peer-reviewed publications including `r ACADEMIC_SUMMARY$pub_count_first` first-author publications. I have received a total of `r ifelse(ACADEMIC_SUMMARY$h_scopus == ACADEMIC_SUMMARY$h_gscholar, glue::glue("{ACADEMIC_SUMMARY$citations_scopus} or {ACADEMIC_SUMMARY$citations_gscholar} citations based on Scopus and Google Scholar, respectively, with an h-index of {ACADEMIC_SUMMARY$h_gscholar} in both sources"), glue::glue("{ACADEMIC_SUMMARY$citations_scopus} or {ACADEMIC_SUMMARY$citations_gscholar} citations and an h-index of {ACADEMIC_SUMMARY$h_scopus} or {ACADEMIC_SUMMARY$h_gscholar} based on Scopus and Google Scholar, respectively"))`.

# EDUCATION 

```{r}
EDUCATION |>
  ## Remove my TXState faux-thesis.
  ## N.B. This 'thesis' is really just the major, defining research project of my undergraduate which I simply want to remember for its impact.
  tidyr::unnest(THESIS) |>
  dplyr::mutate(THESIS = ifelse(INSTITUTION == 'Texas State University',
                                NA_character_,
                                THESIS)) |>
  vitae::detailed_entries(INSTITUTION, 
                          DATES, 
                          DEGREE,
                          embolden(LOCATION), 
                          THESIS,
                          .protect=FALSE)
```

# PROFESSIONAL EXPERIENCE

```{r}
PROFESSIONAL_EXPERIENCE |>
  dplyr::filter(!POSITION %in% c(
    "Independent Research Contractor"
  )) |>
  order_by_date() |>
  vitae::detailed_entries(paste0(INSTITUTION, ": ", DEPARTMENT, " (", TYPE, ")"),
                          DATES,
                          POSITION,
                          embolden(LOCATION),
                          DESCRIPTION,
                          .protect = FALSE)

```

# PUBLICATIONS

## JOURNAL ARTICLES

```{r}
SCOPUS |>
  dplyr::filter(aggregation_type == "Journal",
                !subtype_description %in% c("Book Chapter",
                                            "Conference Paper",
                                            "Erratum")) |>
  vitae::brief_entries(what = glue::glue("{<authors>} ({<substr(cover_date, 1, 4)>}). {<title>}. \\textit{<publication_name>}{<dplyr::case_when(!is.na(volume) & is.na(issue_identifier) ~ glue::glue(', {volume}'), !is.na(volume) & !is.na(issue_identifier) ~ glue::glue(', {volume}({issue_identifier})'), TRUE ~ '')>}{<dplyr::case_when(!is.na(page_range) ~ glue::glue(', {page_range}'), is.na(page_range) & !is.na(article_number) ~ glue::glue(', {article_number}'), TRUE ~ '')>}. \\underline{\\href{<paste0('https://doi.org/', doi)>}{<paste0('doi:', doi)>}}",
                                         .open = "<",
                                         .close = ">"),
                       when = entry_number,
                       with = dplyr::if_else(citedby_count >= 1, 
                                             embolden(glue::glue("{citedby_count} citations")),
                                             ""),
                       .protect = FALSE)

## For reference, this ORCID-based script was used prior to 2023-08
# BIBLIOGRAPHY |>
#   dplyr::filter(TYPE == "journal-article") |>
#   dplyr::filter(!is.na(DATE)) |>
#   order_by_date() |>
#   vitae::brief_entries(glue::glue("\\textbf{<TITLE>} \\newline \\textit{<JOURNAL>}. \\underline{\\href{<DOI_URL>}{<DOI_URL>}}",
#                                   .open = "<",
#                                   .close = ">"),
#                        paste0(substr(DATE, 1, 7), "\\newline"),
#                        # paste0(substr(DATE, 1, 7)),
#                        # embolden(JOURNAL), 
#                        .protect = FALSE)
```

## THESES

```{r}
BIBLIOGRAPHY |>
  dplyr::filter(TYPE == "dissertation-thesis") |>
  order_by_date() |>
  vitae::brief_entries(glue::glue("\\textbf{<TITLE>} \\newline \\textit{<JOURNAL>}. \\underline{\\href{<DOI_URL>}{<DOI>}}",
                                  .open = "<",
                                  .close = ">"),
                       paste0(substr(DATE, 1, 7), "\\newline"),
                       .protect = FALSE)
```

## OPEN-ACCESS DATA

```{r}
BIBLIOGRAPHY |>
  dplyr::filter(TYPE == "data-set") |>
  order_by_date() |>
  vitae::brief_entries(glue::glue("\\textbf{<TITLE>} \\newline \\textit{<JOURNAL>}. \\underline{\\href{<DOI_URL>}{<DOI>}}",
                                  .open = "<",
                                  .close = ">"),
                       paste0(substr(DATE, 1, 7), "\\newline"),
                       # paste0(substr(DATE, 1, 7)),
                       # embolden(JOURNAL), 
                       .protect = FALSE)
```

## SOFTWARE

```{r}
BIBLIO_R |>
  dplyr::arrange(desc(DATE_START), TITLE) |>
  vitae::brief_entries(dplyr::case_when(TYPE == 'public' & !is.na(DATE_END) ~
                                          glue::glue("\\textbf{<TITLE>}: <DESCRIPTION> \\newline <SRC>. \\underline{\\href{<URL>}{<URL>}} (last updated <DATE_END>)",
                                                     .open = "<",
                                                     .close = ">"),
                                        TYPE == 'public' & is.na(DATE_END) ~
                                          glue::glue("\\textbf{<TITLE>}: <DESCRIPTION> \\newline <SRC>. \\underline{\\href{<URL>}{<URL>}}",
                                                     .open = "<",
                                                     .close = ">"),
                                        TRUE ~ 
                                          glue::glue("\\textbf{<TITLE>}: <DESCRIPTION> \\newline <SRC>. \\underline{<TYPE>}",
                                                     .open = "<",
                                                     .close = ">")),
                       paste0(DATE_START, "\\newline"),
                       .protect = FALSE)
```

# HONOURS

## GRANTS AND SCHOLARSHIPS

```{r}
GRANTS |>
  dplyr::filter(TYPE %in% c('grant', 'scholarship')) |>
  order_by_date() |>
  vitae::brief_entries(glue::glue("\\textbf{<TITLE>} \\newline <AGENCY>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       ifelse(!is.na(AMOUNT),
                              embolden(AMOUNT),
                              paste0("")),
                       .protect = FALSE)
```

## AWARDS

```{r, results = "asis"}
AWARDS |>
  dplyr::filter(TYPE == 'award') |>
  order_by_date() |>
  vitae::brief_entries(glue::glue("\\textbf{<TITLE>} \\newline <AGENCY>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       ifelse(!is.na(AMOUNT),
                              embolden(AMOUNT),
                              paste0("")),
                       .protect = FALSE)
```

# CONSULTING

## RESEARCH

```{r, results = "asis"}
CONSULTING_EXPERIENCE |>
  order_by_date() |>
  vitae::brief_entries(glue::glue("\\textbf{<PROJECT>} \\newline <AGENCY>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       embolden(AMOUNT),
                       .protect = FALSE)
```

## MANUSCRIPT REVIEWER

```{r}
MANUSCRIPT_REVIEWS |>
  dplyr::arrange(JOURNAL) |>
  vitae::brief_entries(glue::glue("\\underline{\\textbf{\\textit{\\href{<URL>}{<JOURNAL>}}}} (since <DATE_START>)",
                                  .open = "<",
                                  .close = ">"),
                       .protect = FALSE)
```

# OUTREACH

## CONFERENCES AND PRESENTATIONS

```{r}
OUTREACH |>
  dplyr::filter(TYPE %in% c(
    "professional", "academic", "conference"
  )) |>
  tidyr::unnest(c(URL, URL_TYPE)) |>
  dplyr::group_by(TITLE) |> 
  dplyr::slice(1) |>
  dplyr::ungroup() |>
  dplyr::mutate(LOCATION = stringr::str_remove(LOCATION, "(, Australia|, USA)")) |>
  order_by_date() |> 
  vitae::brief_entries(dplyr::case_when(!is.na(EVENT) & !is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <EVENT> (\\underline{\\href{<URL>}{<URL_TYPE>}})", 
                                                                                 .open = "<", 
                                                                                 .close = ">"),
                                        is.na(EVENT) & !is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <AGENCY> (\\underline{\\href{<URL>}{<URL_TYPE>}})",
                                                                                .open = "<",
                                                                                .close = ">"),
                                        !is.na(EVENT) & is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <EVENT>",
                                                                                .open = "<",
                                                                                .close = ">"),
                                        TRUE ~ glue::glue("\\textbf{<TITLE>} \\newline <AGENCY>", 
                                                          .open = "<", 
                                                          .close = ">")),
                       paste0(substr(DATE, 1, 7), "\\newline"),
                       embolden(LOCATION),
                       .protect = FALSE)
```

## PRESS

```{r}
OUTREACH |>
  dplyr::filter(TYPE %in% c(
    "press"
  )) |>
  dplyr::mutate(LOCATION = stringr::str_remove(LOCATION, "(, Australia|, USA)")) |>
  vitae::brief_entries(glue::glue("\\textbf{<TITLE>} \\newline <AGENCY> (\\underline{\\href{<URL>}{<URL_TYPE>}})",
                                  .open = "<",
                                  .close = ">"),
                       paste0(substr(DATE, 1, 7), "\\newline"),
                       .protect = FALSE)
```

## COURSEWORK

```{r}

OUTREACH |>
  dplyr::filter(TYPE %in% c(
    "coursework"
  )) |>
  tidyr::unnest(c(URL, URL_TYPE)) |>
  dplyr::group_by(TITLE) |> 
  dplyr::slice(1) |>
  dplyr::ungroup() |>
  dplyr::mutate(LOCATION = stringr::str_remove(LOCATION, "(, Australia|, USA)")) |>
  order_by_date() |>
  vitae::brief_entries(dplyr::case_when(!is.na(EVENT) & !is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <EVENT> (\\underline{\\href{<URL>}{<URL_TYPE>}})", 
                                                                                 .open = "<", 
                                                                                 .close = ">"),
                                        is.na(EVENT) & !is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <AGENCY> (\\underline{\\href{<URL>}{<URL_TYPE>}})",
                                                                                .open = "<",
                                                                                .close = ">"),
                                        !is.na(EVENT) & is.na(URL) ~ glue::glue("\\textbf{<TITLE>} \\newline <EVENT>",
                                                                                .open = "<",
                                                                                .close = ">"),
                                        TRUE ~ glue::glue("\\textbf{<TITLE>} \\newline <AGENCY>", 
                                                          .open = "<", 
                                                          .close = ">")),
                       paste0(substr(DATE, 1, 7), "\\newline"),
                       embolden(LOCATION),
                       .protect = FALSE)
```

# VOLUNTEER EXPERIENCE

```{r}
## TODO: Fix order_by_date here. What's going on!?
VOLUNTEER_EXPERIENCE |>
  order_by_date() |>
  vitae::detailed_entries(INSTITUTION,
                          DATES,
                          POSITION,
                          embolden(LOCATION),
                          .protect = FALSE)
```
