---
name: Todd M.
surname: Ellis
position: "Data Analyst & Statistical Programmer"
profilepic: portrait--yee.jpg
address: |
         | Hobart, Tasmania, Australia
phone: +61 466 683 552
email: "toddellis.wa@gmail.com"
linkedin: tmichaelellis
orcid: 0000-0002-4410-8676
researchgate: Todd-Ellis-4
github: toddellis
twitter: tootstorm
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 44B0D1
output: 
  vitae::awesomecv:
    keep_tex: false
    page_total: true
always_allow_html: yes
header-includes:
  \usepackage{float}
  \usepackage{multicol}
  \usepackage{colortbl}
  \arrayrulecolor{white}
  \usepackage{hhline}
  \definecolor{light-gray}{gray}{0.95}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      cache = FALSE)

source(here::here('./scripts/base_data.R'))

## FONTS #### 
.uni <-
  fontawesome::fa('university')
.job <-
  fontawesome::fa('briefcase')
```

# SUMMARY

I'm a data analyst and scientist with a background in the environmental sciences. I've worked in a variety of laboratory and field settings, coordinating research projects for industry reports and scientific journal publication. I've also maintained relational database systems for public and private organizations, developed novel mathematical tools and statistical models for critical management efforts, trained hundreds of students and volunteers in analytical methods and project design, and coordinated project efforts with public and industry managers.

# EDUCATION 

```{r}
EDUCATION |>
  vitae::detailed_entries(UNIVERSITY, DATES, DEGREE, LOCATION,
                   .protect=FALSE)
```

# PROFESSIONAL EXPERIENCE

```{r}
PROFESSIONAL_EXPERIENCE |>
  dplyr::filter(OUTPUT == 'resume') |>
  # dplyr::filter(dplyr::between(ID, max(ID) - 5, max(ID))) |>
  # dplyr::group_by(desc(ID), INSTITUTION, DATES, POSITION) |>
  # dplyr::slice(1:3) |>
  vitae::detailed_entries(INSTITUTION,
                          DATES,
                          POSITION,
                          LOCATION,
                          DESCRIPTION,
                          .protect = FALSE)
```
