---
name: Todd M.
surname: Ellis
position: "Data Analyst & Statistical Programmer"
profilepic: portrait--yee.jpg
address: |
         | Greater Hobart Region, Tasmania, Australia
         | `r format(Sys.time(), '%B %Y')`
aboutme: ""
phone: +61 466 683 552
email: "toddellis.wa@gmail.com"
linkedin: tmichaelellis
googlescholar: q6vTAroAAAAJ
orcid: 0000-0002-4410-8676
researchgate: Todd-Ellis-4
github: toddellis
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 44B0D1
docname: "Résumé"
output: 
  vitae::awesomecv:
    keep_tex: false
    page_total: true
always_allow_html: yes
header-includes:
  \usepackage{float}
  \usepackage{multicol}
  \usepackage{colortbl}
  \usepackage{hhline}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      cache = FALSE)

source(here::here('./scripts/base_data.R'))
  # \arrayrulecolor{white}
  # \definecolor{light-gray}{gray}{0.95}
# twitter: tootstorm
```

# PROFESSIONAL SUMMARY

I’m a data analyst and early career researcher with a varied background in forest ecology, pyrogeography, climate change, geospatial science, and higher education. I've worked as an analyst and researcher in a variety of laboratory, field, and office settings throughout the United States and Australia. Over the course of my career, I've developed novel mathematical tools and statistical models; maintained relational databases and statistical packages used for conducting data analysis and producing standardized reports; trained countless staff, students, and volunteers in institutional policies and procedures, as well as methodological approaches to statistical analysis; and managed both complex and transformative projects for higher education, government agencies, and private industry. My research has been published in high-impact, peer-reviewed journals, and I'm also skilled at conveying complex data and information to both casual and experienced stakeholders. 

# EDUCATION 

```{r}
EDUCATION |>
  vitae::detailed_entries(INSTITUTION, 
                          DATES, 
                          DEGREE,
                          embolden(LOCATION), 
                          .protect=FALSE)
```

# PROFESSIONAL EXPERIENCE

```{r}

PROFESSIONAL_EXPERIENCE |>
  ## Remove those positions that don't quite fit
  dplyr::filter(!POSITION %in% c(
    ## If displaying a consulting section, don't need this
    "Independent Research Contractor"
  )) |>
  tidyr::unnest(DESCRIPTION) |>
  dplyr::group_by(INSTITUTION, DATES, POSITION) |>
  dplyr::slice(1:4) |>
  filter_latest("YEAR_END", 5) |>
  order_by_date() |>
  vitae::detailed_entries(paste0(INSTITUTION, ": ", DEPARTMENT, " (", TYPE, ")"),
                          DATES,
                          POSITION,
                          embolden(LOCATION),
                          DESCRIPTION,
                          .protect = FALSE)

```

# CONSULTING

```{r, results = "asis"}
CONSULTING_EXPERIENCE |>
  ## Does FDL belong here or in consulting?
  # dplyr::filter(AGENCY != "Frontier Development Lab") |>
  # dplyr::arrange(desc(lubridate::as_date(paste0(DATE, '-01'))),
                 # desc(readr::parse_number(AMOUNT))) |>
  vitae::brief_entries(glue::glue("\\textbf{<PROJECT>} \\newline <AGENCY>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       ## Shouldn't include amounts in short-form resume(?)
                       "", # embolden(AMOUNT),
                       .protect = FALSE)
```

# HONOURS

```{r, results = "asis"}
HONOURS |>
  ## Does FDL belong here or in consulting?
  dplyr::filter(AGENCY != "Frontier Development Lab") |>
  filter_latest("DATE", 5) |>
  # dplyr::arrange(desc(lubridate::as_date(paste0(DATE, '-01'))),
  #                desc(readr::parse_number(AMOUNT)))  |>
  vitae::brief_entries(glue::glue("\\textbf{<HONOUR>} \\newline <AGENCY>",
                                  .open = "<",
                                  .close = ">"),
                       paste0(DATE, "\\newline"),
                       ## Shouldn't include amounts in short-form resume(?)
                       "",
                       # ifelse(!is.na(AMOUNT),
                       #        embolden(AMOUNT),
                       #        paste0("")),
                       .protect = FALSE)
```

# VOLUNTEER EXPERIENCE

```{r}
VOLUNTEER_EXPERIENCE |>
  filter_latest("YEAR_END", 5) |>
  dplyr::arrange(desc(YEAR_START)) |>
  vitae::detailed_entries(INSTITUTION,
                          DATES,
                          POSITION,
                          embolden(LOCATION),
                          .protect = FALSE)
```

